Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-04-10 manuscript/manuscript.tex
Started writing new exponential density subsection in manuscript

>>>>

A more complex density variation than a linear one could be an 
exponential function like:

\noindent where $A$, $\Delta h$ and $b$ are constants.
The gravitational potential field generated by a spherical shell with 
this kind of density function on any external point at a distance $r$ 
from its centre can be calculated as follows:

This expression will allow us  to perform comparisons between the 
anaytical solutions and the numerical approximation, similar as the 
ones made for the linear density case.
Although in the exponential density scenario the problem is more 
complex due to the fact that the density-based discretization must be 
used together with the modified adaptive discretization algorithm.
This means that both the distance-size ratio $D$ and the delta ratio 
$\delta$ must be simultaneously determined.

From every $D$ and $\delta$ combination we want to find the one that 
produces a numerical error lower than the 0.1\% threshold while keeping 
an effective computation, i.e. the ($D$, $\delta)$ pair that produces 
the minimum number of discretizations that ensure an acceptable 
numerical precision.
We can propose an heuristic method to perform this task: compute the 
numerical error for every ($D$, $\delta$) points belonging to a grid on 
the $D$, $\delta$ space and specify the pair that combines an 
acceptable numerical error with an efficient computation.

Because the algorithm is intended to work with default $D$ and $\delta$ 
values that ensures these two conditions for every density function, 
the default value for $D$ cannot be lower than the one determined for 
the linear function.
That's why we can only choose the ($D$, $\delta$) points on which
$D \geq D_\text{linear}$.
In this way we can divide the $D$, $\delta$ space in two subregions: 
one with $D < D_\text{linear}$ and other with $D \ge D_\text{linear}$.
The former contains points not eligible, while the latter one will 
contain the one that we want to find.

From the latter subregion we can explore the numerical error of points 
with $D = D_\text{linear}$ and different values of $\delta$.
We will call $\delta_p$ as the maximum $\delta$ at which the numerical 
error is lower than the 0.1\% threshold while keeping
$D = D_ \text{linear}$.
Greater $\delta$ values than $\delta_p$ will produce computations 
with high error, while lower $\delta$ values than $\delta_p$ will 
produce more discretizations leading to non-efficient computation.

With this definition in mind we can subdivide the subregion in two: one 
with points with $\delta > \delta_p$ and other with points with $\delta 
\le \delta_p$.

It worth mention that a greater $D$ or a lower $\delta$ 
increases the number of discretizations of the tesseroid.
Although a greater $D$ may subdivide it in the latitude, longitude 
and/or radial direction; a lower $\delta$ will only discretize the 
original tesseroid in the radial direction.
From this analysis we can conclude that a decrease in $\delta$ will 
produce a more efficient computation than an increase in $D$.

Every point in the subregion with $\delta \le \delta_p$ will have a 
numerical error lower than the 0.1\% threshold, but they will always 
produce more discretizations than the ($\D_\text{linear}$, $\delta_p$) 
point leading to non-efficient computations.

On the other hand, the numerical error of points with $\delta > 
\delta_p$ can either be lower or greater than 0.1\%.
Any point in this subregion with acceptable numerical error will 
produce more discretizations than the ($\D_\text{linear}$, $\delta_p$) 
point, due to $D$ value is increased.
